---
title: "praise-draw analysis"
author: "Mika Asaba"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: true
  pdf_docume9nt:
    toc: yes
  word_document:
    toc: yes
---

Libraries.
```{r echo=FALSE, message=FALSE}
rm(list=ls())

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)

library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(readxl)
library(here)
library(janitor)
```

Counterbalancing info.
1: sp_karen_1, op_linda_2 (selective video first, karen is actress, drawing set 1) 
2: sp_karen_2, op_linda_1
3: sp_linda_1, op_karen_2
4: sp_linda_2, op_karen_1
5: op_karen_1, sp_linda_2
6: op_karen_2, sp_linda_1
7: op_linda_1, sp_karen_2
8: op_linda_2, sp_karen_1

##Pilot 1
Read in file.
```{r, message=FALSE}
p.raw = read_csv("Praisedraw_pilot_2_descriptives_5_25_2019/Praisedraw_AllDescriptives_100_images_final_Praisedraw_pilot_2.csv")

#read in demographics and other coded data
d = read_xlsx("praise-draw_data.xlsx")
```

Combine and clean.
```{r}
all.raw = full_join(p.raw, d)

all.data = all.raw %>%
  select(-session_id, -trial_num, -category, -submit_time, -submit_date, -bounding_box, -filename, -image_name, -count, -date_tested, -bing_ID, -location, -experimenter, -redcap) %>%
  filter(condition == "selective" | condition == "overpraise") %>%
      #   selective_prompt == "anything", overpraise_prompt == "anything") %>%
  mutate(order = ifelse(CB <= 4, "selective_overpraise", "overpraise_selective"),
         age_bin = ifelse(age <5, "4","5"),
         effort_chose_selective = explicit_effort == selective_teacher,
         pref_chose_selective = teacher_pref == selective_teacher) %>%
  rename(id = subID)

d.data.4 = filter(all.data, age_bin == "4")

d.data.5 = filter(all.data, age_bin == "5")
```

Demographics
```{r}
dems = all.data %>%
  summarize(n=n()/2,
            mean_age = mean(age),
            min_age = min(age),
            max_age = max(age))
dems

table(all.data$age_bin)
```


### Tables
```{r}
means.table = all.data %>%
  group_by(condition, age_bin) %>%
  summarize(n=n(),
            m_strokes = mean(num_strokes),
            m_draw_time = mean(draw_duration),
            m_total_time = mean(trial_duration),
            m_intensity = mean(mean_intensity))

means.table
```

### Initial Plots
Number of strokes.
```{r}
ggplot(all.data, aes(x=condition, y=num_strokes)) +
    geom_line(aes(group = id, color=id), size = 0.5) + 
   # geom_jitter(width = .1, height =.1,size = 2)+
  geom_point() +
  theme_few() +
  facet_grid(~ age_bin)

ggplot(means.table, aes(x=condition, y=m_strokes, col=condition)) +
  geom_point(size=5) +
  geom_jitter(data=all.data, aes(x =condition, y =num_strokes, col=condition),width=.1, height=.1,size=1) +
  theme_few() +
  ylab("mean number of strokes") +
  facet_grid(~ age_bin)
```

Draw duration.
```{r}
ggplot(all.data, aes(x=condition, y=draw_duration)) +
    geom_line(aes(group = id, color=id), size = 0.5) + 
    geom_jitter(width = .1, height =.1,size = 2) +
    facet_grid(~ age_bin) +
    theme_few()

ggplot(means.table, aes(x=condition, y=m_draw_time, col=condition)) +
  geom_point(size=3) +
  geom_jitter(data=all.data, aes(x =condition, y =draw_duration),width=.1, height=.1,size=.2) +
  theme_few() +
  ylab("mean time drawing") +
  facet_grid(~ age_bin)
```

Trial duration.
```{r}
ggplot(all.data, aes(x=condition, y=trial_duration)) +
    geom_line(aes(group = id, color=id), size = 0.5) + 
    geom_jitter(width = .1, height =.1,size = 2) +
    facet_grid(~ age_bin)

ggplot(means.table, aes(x=condition, y=m_total_time, col=condition)) +
  geom_point(size=3) +
  geom_jitter(data=all.data, aes(x =condition, y =trial_duration),width=.1, height=.1,size=.2) +
  theme_few() +
  ylab("mean total time") +
  facet_grid(~ age_bin)
```

Amount of ink (intensity).
```{r}
ggplot(all.data, aes(x=condition, y=mean_intensity)) +
    geom_line(aes(group = id, color=id), size = 0.5) + 
    geom_jitter(width = .01, height =.01,size = 2) +
  facet_grid(~ age_bin)

ggplot(means.table, aes(x=condition, y=m_intensity, col=condition)) +
  geom_point(size=3) +
  geom_jitter(data=all.data, aes(x =condition, y =mean_intensity),width=.1, height=.1,size=.2) +
  theme_few() +
  ylab("mean intensity") +
  facet_grid(~ age_bin)
```

### Analyses
```{r}
summary(lmer(num_strokes ~ condition * age + order + (1|id), data=all.data))
summary(lmer(draw_duration ~ condition * age + order + (1|id), data=all.data))
summary(lmer(mean_intensity ~ condition * age + order + (1|id), data=all.data))

t.test(num_strokes ~ condition, all.data, paired=TRUE)
```

### Explicit questions
```{r}
explicit.table = d.data %>%
  group_by(age_bin) %>%
  summarize(num_effort_chose_selective = sum(effort_chose_selective),
            num_pref_chose_selective = sum(pref_chose_selective),
            n=n())

explicit.table

```

##Pilot 2
Read in file.
```{r, message=FALSE}
p2.raw = read_csv("Praisedraw_pilot_3_descriptives_7_17_2019/descriptives_merged_pilot_3_4.csv")

#read in demographics and other coded data
d = read_xlsx("praise-draw_data.xlsx",sheet=2)
```

Combine and clean.
```{r}
all.raw = full_join(p2.raw,d) # change this later to combine w/ demographics data sheet

all.data = all.raw %>%
  select(-session_id, 
         -trial_num, 
         -category, -submit_time, -submit_date, -bounding_box, -filename, -image_name,
         -count, 
         -date_tested, 
         -bing_ID, 
         -location, 
         -experimenter, 
         -redcap) %>%
  filter(condition == "tryit" | condition == "selective" | condition == "overpraise",
         subID != "PD2_190715_04") %>% #didn't do selective teacher drawing
      #   selective_prompt == "anything", overpraise_prompt == "anything") %>%
  mutate(order = ifelse(CB <= 4, "selective_overpraise", "overpraise_selective"),
         age_bin = ifelse(age <5, "4","5"),
         effort_chose_selective = explicit_effort == selective_teacher,
         pref_chose_selective = teacher_pref == selective_teacher) %>%
  rename(id = subID)
```

### Tables
Table with counts for # of drawings for each teacher.
```{r}
id.table = all.data %>%
  group_by(age_bin,order,id) %>%
  summarise(#n_try = sum(condition == "tryit"),
            sp=sum(condition == "selective"),
            op = sum(condition =="overpraise"))

id.table

id.tidy = id.table %>%
  gather(teacher, practices, sp, op)

```

### Initial Plots
```{r}
ggplot(id.tidy, aes(x=teacher, y=practices)) +
    geom_line(aes(group = id, color=id), size = 0.5) + 
   # geom_jitter(width = .1, height =.1,size = 2)+
  geom_point() +
  theme_few() +
  facet_grid(order ~ id)
```

### Explicit questions
```{r}
explicit.table = all.data %>%
  group_by(id) %>%
  summarize(num_effort_chose_selective = sum(effort_chose_selective),
            num_pref_chose_selective = sum(pref_chose_selective),
            n=n())

explicit.table

```

##Pilot 3
Read in file.
```{r, message=FALSE}
p3.raw = read_csv("merged_summer_pilot.csv")

#read in demographics and other coded data
d = read_xlsx("praise-draw_data.xlsx",sheet=2)
```

Combine and clean.
```{r}
all.raw = full_join(p3.raw,d) 

all.data = all.raw %>%
  select(-session_id, 
         -trial_num, 
         -category, -submit_time, -submit_date, -bounding_box, -filename, -image_name,
         -count, 
         -date_tested, 
         -bing_ID, 
         -location, 
         -experimenter, 
         -redcap) %>%
  filter(condition == "tryit" | condition == "selective" | condition == "overpraise",
         subID != "PD2_190715_04",
         subID != "PD_190712_03",
         age >= 4) %>% #didn't do selective teacher drawing
    #     drawing2_prompt == "flower",
    #     drawing1_prompt == "flower") %>% 
      #   selective_prompt == "anything", overpraise_prompt == "anything") %>%
  mutate(order = ifelse(CB <= 4, "selective_overpraise", "overpraise_selective"),
         effort_chose_selective = explicit_effort == selective_teacher,
         pref_chose_selective = teacher_pref == selective_teacher) %>%
  rename(id = subID)
```

### Demographics
```{r}
dems = all.data %>%
  group_by(id) %>%
  summarize(age = mean(age)) %>%
  ungroup() %>%
  na.omit() %>%
  summarize(n=n(),
            mean_age = mean(age),
            min_age = min(age),
            max_age = max(age))

dems

dems_age = all.data %>%
  group_by(age_bin) %>%
  summarize(n = n_distinct(id))
  
dems_age
```

### Re-dos
Table with counts for # of re-dos for each teacher.
```{r}
redo.table = all.data %>%
  group_by(age, age_bin,order,id) %>%
  summarise(sp=sum(condition == "selective"),
            op = sum(condition =="overpraise")) %>%
  gather(teacher, n_practices,sp, op) %>%
  na.omit()

redo.means = redo.table %>%
  group_by(teacher) %>%
  summarise(mean = mean(n_practices))

redo.means.age = redo.table %>%
  group_by(teacher,age_bin) %>%
  summarise(mean = mean(n_practices))
```

Plot of counts for # of re-dos for each teacher.
```{r}
ggplot() +
  geom_jitter(data=redo.table, aes(x=teacher, y=n_practices,col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=redo.means, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

#split by age
ggplot() +
  geom_jitter(data=redo.table, aes(x=teacher, y=n_practices,col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=redo.means.age, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12)) +
  facet_grid(~ age_bin)

#age on x-axis
ggplot() +
  geom_jitter(data=redo.table, aes(x=age, y=n_practices,col=teacher), size=1, width=.2, height=.1) +
 # geom_point(data=redo.means.age, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))
 # facet_grid(~ age_bin)
```

Table with differences in # re-dos.
```{r}
redo.diff.data = all.data %>%
  group_by(age, age_bin,order,id) %>%
  summarise(sp=sum(condition == "selective"),
            op = sum(condition =="overpraise"),
            diff = sp-op) %>%
  mutate(more = ifelse(diff > 0, "sp",ifelse(diff == 0, "same", ifelse(diff < 0, "op","")))) %>%
  na.omit()

redo.diff.tidy = redo.diff.data %>%
  group_by(age_bin, order) %>%
  summarise(n_sp = sum(more == "sp"),
            n_op = sum(more == "op"),
            same = sum(more == "same")) %>%
  gather(type, count, n_sp, n_op, same) %>%
  mutate(type = factor(type, levels=c("n_sp","n_op","same"), labels=c("more_sp", "more_op","same")))


```

Plot with differences in # re-dos.
```{r}
ggplot(redo.diff.tidy, aes(x=type, y=count,fill=type)) +
  geom_bar(stat="identity") +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  facet_grid(~ age_bin) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))
 # facet_grid(~age_bin)

#age on x-axis
ggplot() +
  geom_jitter(data=redo.diff.data, aes(x=age, y=diff, col=more), size=1, width=.2, height=.1) +
 # geom_point(data=redo.means.age, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  facet_grid(~ order)
```

#### Analyses
```{r}
summary(lmer(n_practices ~ teacher + order + age + (1|id), data=redo.table))
summary(lmer(n_practices ~ teacher * age + order + (1|id), data=redo.table))
```

```{r}
summary(lmer(time ~ teacher * order * age + (1|id), data=time.tidy))

summary(lmer(practices ~ teacher * age + (1|id), data=id.tidy))

summary(lmer(strokes ~ teacher + order + (1|id), data=strokes.tidy))

```

```{r}
redo.table = all.data %>%
  group_by(age, age_bin,order,id) %>%
  summarise(sp=sum(condition == "selective"),
            op = sum(condition =="overpraise"),
            diff = sp-op) %>%
  mutate(more = ifelse(diff > 0, "sp",ifelse(diff == 0, "same", ifelse(diff < 0, "op","")))) %>%
  na.omit()


redo.table

redo.counts = redo.table %>%
  group_by(age_bin, order) %>%
  summarise(n_sp = sum(more == "sp"),
            n_op = sum(more == "op"),
            same = sum(more == "same"))

redo.counts



id.counts2 = id.counts %>%
  gather(type, count, n_sp, n_op, same) %>%
  mutate(type = factor(type, levels=c("n_sp","n_op","same"), labels=c("More for Selective", "More for Overpraise","Same for each")))

ggplot(id.counts2, aes(x=type, y=count,fill=type)) +
  geom_bar(stat="identity") +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  facet_grid(~ age_bin) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

id.means = id.table %>%
  gather(teacher, practices, sp, op) %>%
  group_by(age_bin,teacher) %>%
  summarize(n=n(),
            m_practices = mean(practices))

id.means

id.tidy = id.table %>%
  gather(teacher, practices, sp, op)

id.tidy

ggplot() +
  geom_point(data=id.means, aes(x=teacher, y=m_practices, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=id.tidy, aes(x=teacher, y=practices), size=.5, width=.1, height=.1) +
    theme_few() +
  ylab("Number of re-dos") +
  facet_grid(~ age_bin)

ggplot() +
#  geom_point(data=id.table, aes(x=teacher, y=m_practices, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=id.table, aes(x=age_bin, y=diff,col=more), size=2, width=.2, height=.1) +
    theme_few() +
  ylab("Difference in number of re-dos") +
  facet_grid(~ age_bin) +
  geom_hline(yintercept=0,linetype="dashed",size=.5)

ggplot() +
#  geom_point(data=id.table, aes(x=teacher, y=m_practices, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=id.table, aes(x=age, y=diff,col=more), size=1.5, width=.2, height=.1) +
    theme_few() +
  ylab("Difference in number of re-dos") +
  facet_grid(~ age_bin) +
  geom_hline(yintercept=0,linetype="dashed",size=.5)
```

### Time
Table with tracing time.
```{r}
trace.data = all.raw %>%
  select(-session_id, 
         -trial_num, 
         -submit_time, -submit_date, -bounding_box, -filename, -image_name,
         -count, 
         -date_tested, 
         -bing_ID, 
         -location, 
         -experimenter, 
         -redcap) %>%
  filter(condition == "tracing",
         subID != "PD2_190715_04",
         subID != "PD_190712_03") %>%
  rename(id = subID) %>%
  mutate(category = factor(category, levels=c("this square","this shape"), labels=c("square","complex")))

trace.table = trace.data %>%
  group_by(age_bin,category) %>%
  summarise(avg_time = mean(draw_duration),
            min_time = min(draw_duration),
            max_time = max(draw_duration))
```

```{r}
#calculate total time
overpraise.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "selective") %>%
  spread(condition, draw_duration) %>%
  select(age,age_bin, order, id, overpraise)%>%
  group_by(id, age, age_bin, order) %>%
  summarize(m_overpraise = mean(overpraise))

selective.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "overpraise") %>%
  spread(condition, draw_duration) %>%
  select(age, age_bin, order, id, selective)%>%
  group_by(id,order) %>%
  summarize(m_selective = mean(selective))

time.table = full_join(overpraise.table, selective.table)

time.tidy = time.table %>%
  gather(teacher, time, m_overpraise, m_selective)

time.means = time.tidy %>%
  group_by(teacher) %>%
  na.omit() %>%
  summarize(mean = mean(time))
```

```{r}
ggplot() +
  geom_jitter(data=time.tidy, aes(x=teacher, y=time, col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=time.means, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE)
#  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

#split by age
ggplot() +
  geom_jitter(data=time.tidy, aes(x=teacher, y=time, col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=time.means, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  facet_grid(~ age_bin)
```

```{r}
time.table = time.table %>%
    group_by(age_bin) %>%
  mutate(diff = m_selective - m_overpraise,
         more = ifelse(diff > 0, "sp","op"))

time.counts = time.table %>%
  group_by(age_bin) %>%
  summarise(n_sp = sum(more == "sp"),
            n_op = sum(more == "op")) %>%
  gather()
time.counts

ggplot(time.table, aes(x=more, y=count,fill=more)) +
  geom_bar(stat="identity") +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  facet_grid(~ age_bin) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

ggplot() +
#  geom_point(data=id.table, aes(x=teacher, y=m_practices, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=time.table, aes(x=age_bin, y=diff,col=more_sp), size=1.5, width=.2, height=.1) +
    theme_few() +
  ylab("Difference in draww duration (Selective - Overpraise)") +
#  facet_grid(~ age_bin) +
  geom_hline(yintercept=0,linetype="dashed",size=.5)


time.tidy = time.table %>%
  gather(teacher, time, m_selective, m_overpraise)

time.means = time.tidy %>%
  group_by(teacher) %>%
  summarize(mean_time = mean(time))

time.means

ggplot() +
  geom_point(data=time.means, aes(x=teacher, y=mean_time, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=time.tidy, aes(x=teacher, y=time), size=.5, width=.1, height=.1) +
    theme_few() +
  ylab("Amount of time (seconds)")


ggplot() +
#  geom_point(data=id.table, aes(x=teacher, y=m_practices, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=id.table, aes(x=age, y=diff), size=.5, width=.1, height=.1) +
    theme_few() +
  ylab("Number of re-dos") +
  geom_hline(yintercept=0)
```

#### Analyses
```{r}
summary(lmer(time ~ teacher * order + age + (1|id), data=time.tidy))
```

### Number of strokes
```{r}
overpraise.table = all.data %>%
  group_by(age, age_bin,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "selective") %>%
  spread(condition, num_strokes) %>%
  select(age,age_bin, order, id, overpraise)%>%
  group_by(id, age_bin, order) %>%
  summarize(m_overpraise = mean(overpraise))

selective.table = all.data %>%
  group_by(age,age_bin,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "overpraise") %>%
  spread(condition, num_strokes) %>%
  select(age, age_bin, order, id, selective)%>%
  group_by(id,age_bin,order) %>%
  summarize(m_selective = mean(selective))

strokes.table = full_join(overpraise.table, selective.table)

strokes.tidy = strokes.table %>%
  gather(teacher, strokes, m_selective, m_overpraise)

strokes.means = strokes.tidy %>%
  group_by(order,teacher) %>%
  summarize(mean_strokes = mean(strokes))

strokes.means

ggplot() +
  geom_point(data=strokes.means, aes(x=teacher, y=mean_strokes, col=teacher, size=4)) +
#  ylim(0,4) +
  geom_jitter(data=strokes.tidy, aes(x=teacher, y=strokes), size=.5, width=.1, height=.1) +
    theme_few() +
  ylab("Number of strokes") +
  facet_grid(age_bin ~ order)
```

### Analyses
```{r}
summary(lmer(time ~ teacher * order * age + (1|id), data=time.tidy))

summary(lmer(practices ~ teacher * age + (1|id), data=id.tidy))

summary(lmer(strokes ~ teacher + order + (1|id), data=strokes.tidy))
```

### Between-subjects
Number of redos.
```{r}
bw.redo.table = redo.table %>%
  filter((order == "selective_overpraise" & teacher == "sp") | order == "overpraise_selective" & teacher == "op")

bw.redo.means = bw.redo.table %>%
  group_by(age_bin,teacher) %>%
  summarize(n=n(),
            mean = mean(n_practices))

ggplot() +
  geom_jitter(data=bw.redo.table, aes(x=teacher, y=n_practices,col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=bw.redo.means, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE) +
  scale_y_continuous(breaks=c(0,2,4,6,8,10,12)) +
  facet_grid(~ age_bin)

summary(lm(n_practices ~ teacher * age, data=bw.redo.table))
```

Time.
```{r}
overpraise.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "selective") %>%
  spread(condition, draw_duration) %>%
  select(age,age_bin, order, id, overpraise)%>%
  group_by(id, order) %>%
  filter(order == "overpraise_selective") %>%
  summarize(age = mean(age),
            time = mean(overpraise),
            #redos = sum(condition == "overpraise"),
            teacher = "overpraise")

selective.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "overpraise") %>%
  spread(condition, draw_duration) %>%
  select(age, age_bin, order, id, selective)%>%
  group_by(id,order) %>%
  filter(order == "selective_overpraise") %>%
  summarize(age = mean(age),
            time = mean(selective),
            teacher = "selective")

bw.table.time = full_join(overpraise.table, selective.table)
bw.table.older.time = filter(bw.table, age >= 5)
```

Table with time spent for each teacher.
```{r}
time.means = bw.table %>%
  group_by(teacher) %>%
  summarise(mean = mean(time))
```

Plot of time for each teacher.
```{r}
ggplot() +
  geom_jitter(data=bw.table, aes(x=teacher, y=time,col=teacher), size=1, width=.2, height=.1) +
  geom_point(data=time.means, aes(x=teacher, y=mean), size=4) +
  xlab("") +
  theme_few() +
  guides(fill=FALSE)
#  scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

summary(lm(time ~ teacher * age, data=bw.table))
summary(lm(time ~ teacher + age, data=bw.table.older))
```

Number of strokes.
```{r}
overpraise.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "selective") %>%
  spread(condition, num_strokes) %>%
  select(age,age_bin, order, id, overpraise)%>%
  group_by(id, order) %>%
  filter(order == "overpraise_selective") %>%
  summarize(age = mean(age),
            strokes = mean(overpraise),
            #redos = sum(condition == "overpraise"),
            teacher = "overpraise")

selective.table = all.data %>%
  group_by(age_bin,order,id) %>%
  filter(condition != "tracing", condition != "tryit", condition != "overpraise") %>%
  spread(condition, draw_duration) %>%
  select(age, age_bin, order, id, selective)%>%
  group_by(id,order) %>%
  filter(order == "selective_overpraise") %>%
  summarize(age = mean(age),
            time = mean(selective),
            teacher = "selective")

bw.table.time = full_join(overpraise.table, selective.table)
bw.table.older.time = filter(bw.table, age >= 5)
```



```{r}
ggplot(bw.table, aes(x=teacher, y=time)) +
   # geom_jitter(width = .1, height =.1,size = 2)+
  geom_boxplot() +
  theme_few()

#plot with older kids
ggplot(bw.table.older, aes(x=teacher, y=time)) +
    geom_jitter(width = .1, height =.1,size = 2)+
  theme_few()

time.table = left_join(time.table, d)
time.tidy = time.table %>%
  gather(teacher, time, m_selective, m_overpraise)

time.tidy
```

### Explicit questions
```{r}
questions.data = d %>%
    mutate(effort_teacher = explicit_effort == selective_teacher,
         preference_teacher = teacher_pref == selective_teacher,
         improve_teacher = get_better == selective_teacher,
         id = subID,
         effort_exp = explicit_effort_explanation,
         preference_exp = teacher_pref_explanation,
         improve_exp = get_better_explanation) %>%
  select(id, age, age_bin, effort_teacher, effort_exp, preference_teacher, preference_exp, improve_teacher, improve_exp)

questions.means = d %>%
  group_by(age_bin) %>%
  summarize(n=n(),
            effort_sp = sum(explicit_effort == selective_teacher)/n,
            pref_sp = sum(teacher_pref == selective_teacher)/n,
            improve_sp = sum(get_better == selective_teacher)/n)
  
ggplot
```
